\pkg{cv}: An \proglang{R} Package for Cross-Validating Regression Models

### 2024-07-11 scratch/notes_john/JSS-article/JSS-article-4.Rmd
improve C+R plots in JSS-article-4

m.auto <- lm(mpg ~ ., data = Auto)
crPlots(m.auto, pch = ".")
```

@@

We start with a "working model" that specifies linear partial relationships of the response to the numeric predictors:
```{r Auto-working-model, eval=FALSE}
m.auto <- lm(mpg ~ ., data = Auto)
crPlots(m.auto, pch = ".")
```
The component + residual (C+R) plots in Figure \ref{fig:Auto-explore} (b), produced by the \code{cvPlots()} function in the \pkg{car} package, clearly reveal the inadequacy of the model. The broken blue lines in the C+R plots show linear least-squares fits, while the solid magenta lines are nonparametric-regression smooths.

@@

The transformed numeric variables are much better-behaved (cf., Figure \ref{fig:Auto-explore} (a), on page \pageref{fig:Auto-explore}, and Figure \ref{fig:Auto-transformed} (a)):
```{r Auto-transformed, fig.show="hold", echo=FALSE}
#| out.width = "65%",
#| fig.align = 'center',
#| fig.height = 4.5,
#| fig.ncol = 1,
#| fig.cap = "(a) Scatterplot matrix for the transformed numeric variables in the \\code{Auto} data. (b) Component + residual plots for the regression model fit to the transformed \\code{Auto} data.",
#| fig.subcap=rep("", 2)
scatterplotMatrix(~ log(mpg) + displacement + horsepower + weight 
                  + acceleration, 
                  smooth=list(spread = FALSE), data = A, pch = ".")
crPlots(m, pch = ".")
```

@@

And the partial relationships in the model fit to the transformed data are much more nearly linear (cf., Figure \ref{fig:Auto-explore} (b), on page \pageref{fig:Auto-explore}, and Figure \ref{fig:Auto-transformed} (b)):
```{r Auto-CR-plots-transformed, eval=FALSE}
crPlots(m, pch = ".")
```

>>>>

m.auto <- lm(mpg ~ ., data = Auto)
crPlots(m.auto, pch = ".", ylab = "C+R", las = 2)
```

@@

We start with a "working model" that specifies linear partial relationships of the response to the numeric predictors:
```{r Auto-working-model, eval=FALSE}
m.auto <- lm(mpg ~ ., data = Auto)
crPlots(m.auto, pch = ".", ylab = "C+R", las = 2)
```
The component + residual (C+R) plots in Figure \ref{fig:Auto-explore} (b), produced by the \code{cvPlots()} function in the \pkg{car} package, clearly reveal the inadequacy of the model. The broken blue lines in the C+R plots show linear least-squares fits, while the solid magenta lines are nonparametric-regression smooths.

@@

The transformed numeric variables are much better-behaved (cf., Figure \ref{fig:Auto-explore} (a), on page \pageref{fig:Auto-explore}, and Figure \ref{fig:Auto-transformed} (a)):
```{r Auto-transformed, fig.show="hold", echo=FALSE}
#| out.width = "65%",
#| fig.align = 'center',
#| fig.height = 4.5,
#| fig.ncol = 1,
#| fig.cap = "(a) Scatterplot matrix for the transformed numeric variables in the \\code{Auto} data. (b) Component + residual plots for the regression model fit to the transformed \\code{Auto} data.",
#| fig.subcap=rep("", 2)
scatterplotMatrix(~ log(mpg) + displacement + horsepower + weight 
                  + acceleration, 
                  smooth=list(spread = FALSE), data = A, pch = ".")
crPlots(m.auto, pch = ".", ylab = "C+R", las = 2)
```

@@

And the partial relationships in the model fit to the transformed data are much more nearly linear (cf., Figure \ref{fig:Auto-explore} (b), on page \pageref{fig:Auto-explore}, and Figure \ref{fig:Auto-transformed} (b)):
```{r Auto-CR-plots-transformed, eval=FALSE}
crPlots(m.auto, pch = ".", ylab = "C+R", las = 2)
```
